---
title: "Hierarchial_Clustering"
author: "Poro Burman"
date: "8/26/20"
output:
  pdf_document: default
  html_document: default
---

# Introduction    

The purpose of this script is to find a pattern amongst the customers visiting a Mall.    
The dataset used in this script consists of customers data collected by a Mall.    
Each row consists of a customer. Each column consists of a customer's variable,    
including his/her spending score.    

# 1. Data pre-processing    

Import the dataset    
```{r}
dataset = read.csv('Mall_Customers.csv')
```    
Select the variables to perform clustering on
```{r}
X <- dataset[4:5]
```    
print top 5 dataset values
```{r}
head(dataset)
```    

# 2. Select number of clusters    
```{r}
dendogram <- hclust(dist(X, 
                        method = 'euclidean'),
                        method = 'ward.D')

plot(dendogram,
     main = paste("Dendogram"),
     xlab = "Customers",
     ylab = 'Euclidean distance')
```    

from the elbow plot, I'm selecting 5 clusters for further downstream analysis.    

# 3. Training Hierarchial clustering model on the dataset    
```{r}
hc <- hclust(dist(X, method = 'euclidean'), method = 'ward.D')

y_hc = cutree(hc, 5)
```    

# 4. Visualize the clusters    
```{r}
library(cluster)

clusplot(X,
         y_hc,
         lines = 0,
         shade = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = "Annual Income",
         ylab = "Spending Score")
```    

As you can see, different clusters show the customers who have different annual incomes    
and their related spending scores. This can be used to target certain specific customers    
based upon these clusters.